### 2021-07-15 src/paper/model/code.tex

We are grateful to the authors and contributors of the following software packages upon
which our software is built: conda \cite{Anaconda2016}, conda-forge
\cite{CondaForge2015} dask \cite{Rocklin2015}, estimagic \cite{Gabler2020a}, holoviews
\cite{Stevens2015}, matplotlib \cite{Hunter2007}, numba \cite{Lam2015}, numpy
\cite{Harris2020}, pandas \cite{Reback2020,McKinney2010}, pytask \cite{Raabe2020},
Python \cite{VanRossum1995}, scipy \cite{Virtanen2020}.

>>>>

We are grateful to the authors and contributors of the following software packages upon
which our software is built: conda \cite{Anaconda2016}, conda-forge
\cite{CondaForge2015} dask \cite{Rocklin2015}, estimagic \cite{Gabler2020a}, holoviews
\cite{Stevens2015}, matplotlib \cite{Hunter2007}, numba \cite{Lam2015}, numpy
\cite{Harris2020}, pandas \cite{Reback2020,McKinney2010}, pytask \cite{Raabe2020},
Python \cite{VanRossum1995}, scipy \cite{Virtanen2020}, and seaborn \cite{Waskom2021}.
